Opportunities for improvement in the care of adult trauma patients arriving

### 2024-11-28 manuscript.Rmd
försökt åtgärda ref funktionen men inte fått till de.

---
title: "Opportunities for improvement in the care of adult trauma patients arriving in shock"
author: "Carl Skog"
output:
  html_document: default
  word_document: default
bibliography: bibliography.bib
csl: vancouver.csl
---

@@

## Shock classifications
Out of the clinical needs to assess the severity of trauma shock, patients can be categorized by stratifying symptoms and physiological parameters into degrees. Many different scoring systems have been developed, such as ATLS classification for hemorrhagic shock (See Table \@ref(tab:alts) [@noauthor_atls_2018], Trauma Associated Severe Hemorrhage (TASH) and Assessment of Blood Consumption (ABC) scores for predicting massive transfusion [@el-menyar_review_2019]. While none of these systems comprehensively classifies shock severity across all types of trauma shock, each aid in assessing severity through core physiological indicators. Ultimately, these classifications rely on vital signs and clinical indicators, highlighting the importance of physiological metrics in evaluating shock severity across clinical settings.

>>>>

---
title: Opportunities for improvement in the care of adult trauma patients arriving
  in shock
author: "Carl Skog"
output:
  word_document: default
  pdf_document: default
  html_document: default
bibliography: bibliography.bib
csl: vancouver.csl
---

@@

## Shock classifications
Out of the clinical needs to assess the severity of trauma shock, patients can be categorized by stratifying symptoms and physiological parameters into degrees. Many different scoring systems have been developed, such as ATLS classification for hemorrhagic shock (See Table \@ref(tab:alts) [@noauthor_atls_2018]), Trauma Associated Severe Hemorrhage (TASH) and Assessment of Blood Consumption (ABC) scores for predicting massive transfusion [@el-menyar_review_2019]. While none of these systems comprehensively classifies shock severity across all types of trauma shock, each aid in assessing severity through core physiological indicators. Ultimately, these classifications rely on vital signs and clinical indicators, highlighting the importance of physiological metrics in evaluating shock severity across clinical settings.
